Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-26 paper/ms.tex
update manuscript

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black
  circles), and stars in the neighborhood (gray circles).} Members
  were identified by \citet{cantatgaudin_gaia_2018}.  $\alpha$ denotes
  right ascension, $\delta$ declination, $\pi$ parallax, $\mu_{\rm
  \delta}$ and $\mu_{\rm \alpha}$ proper motion in each equatorial
  direction, and ${\rm RV}$ radial velocity reported by Gaia DR2.  The
  RVs are for unblended spectra of bright stars ($G\lesssim 12$).  The
  proper motion projection ($\mu_{\delta}$ vs{.} $\mu_{\rm
  \alpha}\cos\delta$) highlights incompleteness in the membership selection function.
  \label{fig:full_kinematics}
	}
\end{figure*}

@@

\subsubsection{Physical Characteristics}

@@

The star is clearly a rapid rotator.
Figure~\ref{fig:lithium_rotation} compares its rotation period with
rotation periods that have been measured in a number of well-studied
open clusters.  \tn\ seems to be gyrochronologically coeval with the
Pleiades sequence.  This is not to say that \tn\ is ``Pleaides-aged'',
because the observed scatter in the rotation-period diagram for the
first 10--100$\,$Myr is quite high \citep[see Figure~9
of][]{rebull_rotation_2020}.  Instead, we interpret it as a piece of
evidence to support the claim that \tn\ is younger than $\sim
500\,{\rm Myr}$.

@@

We measured the physical properties of \tn\ as follows.

The spectroscopic parameters were measured from each of the six CHIRON
spectra (Section~\ref{subsec:chiron}). We then averaged the results,
and adopted the standard deviation across the spectra as the
uncertainty.

This yielded:
\begin{align}
  T_{\rm eff}   &= 5946 \pm 39\,{\rm K}, \nonumber \\
  \log g        &= 4.48 \pm 0.03, \nonumber \\
  {\rm [Fe/H] } &= -0.065 \pm 0.035, \nonumber \\
  v \sin i      &= 17.48 \pm 0.15\,{\rm km\,s}^{-1}.
\end{align}
These spectroscopic parameters were used in our final analysis of the
system (Section~\ref{sec:system}).

 (Lstar, Rstar, Teff, Age and Mstar)

From CHIRON spectra, my current best guess spectroscopic parameters
 are as follows.
 Teff = 5946 +/- 39
 logg = 4.48 +/- 0.03
 feh = -0.065 +/- 0.035
 vsini = 17.48 +/- 0.15

% Figure~\ref{fig:sed}.
Mention The SED fit, looking really good with rchi2 = 1.6:

The fit parameters are: 
Av = 0.20 +/- 0.03
Fbol = 1.967 +/- 0.046 e-9 erg/s/cm2 
Rstar = 1.049 +/- 0.019 Rsun

From the spectroscopic logg and the above Rstar, we get an independent
mass estimate of 
Mstar = 1.21 +/- 0.10 Msun 
At face value, the mass seems a bit high for the radius, but I'm
guessing that just means the spectroscopic logg is a bit too high.

\subsubsection{Rotation}
Stellar vsini
Stellar rotation

\subsubsection{RVs}
I don't strongly expect the Veloce RVs or the FEROS ones to lead to a
mass measurement. The reason is that with vsini=17km/s, and 2\%
rotation amplitude signal, we expect an RV RMS of 300m/s at the
Prot=3.5 day rotation period (vsini*rotation amplitude). This is
probably larger than the expected planet signal (100m/s, 8 days).

@@

@@

>>>>

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.7\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black
  circles), and stars in the neighborhood (gray circles).} Members
  were identified by \citet{cantatgaudin_gaia_2018}.  $\alpha$ denotes
  right ascension, $\delta$ declination, $\pi$ parallax, $\mu_{\rm
  \delta}$ and $\mu_{\rm \alpha}$ proper motion in each equatorial
  direction, and ${\rm RV}$ radial velocity reported by Gaia DR2.  The
  RVs are for unblended spectra of bright stars ($G\lesssim 12$).  The
  proper motion projection ($\mu_{\delta}$ vs{.} $\mu_{\rm
  \alpha}\cos\delta$) highlights incompleteness in the membership selection function.
  \label{fig:full_kinematics}
	}
\end{figure*}

@@

\subsubsection{Physical Characteristics}
\label{subsec:clusterchar}

@@

The star is clearly a rapid rotator.
Figure~\ref{fig:lithium_rotation} compares its rotation period with
rotation periods that have been measured in a number of well-studied
open clusters.  \tn\ seems to be gyrochronologically coeval with the
Pleiades sequence.  This is not to say that \tn\ is ``Pleaides-aged'',
because the observed scatter in the rotation-period diagram for the
first 10--100$\,$Myr is quite high \citep[see Figure~9
of][]{rebull_rotation_2020}.  Instead, we interpret the rotation
period as evidence to support the claim that \tn\ is younger than $\sim$
$500\,{\rm Myr}$.

@@

Select properties of \tn\ from the literature and our analysis are
presented in Table~\ref{tab:starparams}.  The spectroscopic parameters
were measured from each of the six CHIRON spectra
(Section~\ref{subsec:chiron}). We then averaged the results, and
adopted the standard deviation across the spectra as the uncertainty.

We then calculated the stellar radius and reddening following
\citet{stassun_accurate_2017}.  We first derived the bolometric flux
by combining available broadband magnitudes from Gaia, Tycho-2, APASS,
2MASS, and WISE.  We then fitted the SED with the
\citet{kurucz_atlas12_2013} stellar atmopshere models, and summed to
find $F_{\rm bol}$.  When fitting the atmosphere model, we varied the
extinction ($A_{\rm V}$) and the overall normalization.  This
procedure yielded $A_{\rm V} = 0.20\pm0.03$, which independently
agrees with the average from the \cn\ isochrone fits of
\citet{randich_gaiaeso_2018}.
We then combined the spectroscopic effective temperature, bolometric
flux, and Gaia distance to determine the stellar radius, using the
Stefan-Boltzmann law.

@@

To derive physical parameters of \pn\ based on the photometry, we
fitted the TESS and ground-based transits simultaneously.

@@

I don't strongly expect the Veloce RVs or the FEROS ones to lead to a
mass measurement. The reason is that with vsini=17km/s, and 2\%
rotation amplitude signal, we expect an RV RMS of 300m/s at the
Prot=3.5 day rotation period (vsini*rotation amplitude). This is
probably larger than the expected planet signal (100m/s, 8 days).
